|

### 2016-06-01 manuscript/manuscript_wtc3.Rmd
change hypo

\
4.	The effects of climate warming were predicted to be greater in sun than shade leaves, seen as a decrease in g~s~ and leaf C gain during summer months, as increased evaporation demand from higher temperatures lead to stomatal closure.

as higher temperatures

@@

\
Leaf level gas exchange was measured with a standard (2 x 3 cm) leaf cuvette using a portable gas exchange system (LI-6400XT, LI-COR, Lincoln, NE, USA). This system was coupled with a tunable diode laser (TDL; TGA100,Campbell Scientific, Inc., Logan, UT, USA) for concurrent measurements of online C isotope discrimination. The CO~2~ in the leaf cuvette was set at ambient atmospheric [CO~2~] (400 ppm) with a flow rate of 200 $\mu$mol s^-1^. We did not explicitly control relative humidity within the leaf cuvette. Two identical gas exchanges systems were run simultaneously, one in each of an AT or ET WTC. Leaf temperatures were controlled at the current AT or ET WTC air temperature. PPFD in the cuvette was set to match the individual light environment of each leaf type (explained above). Periods of high irradiance were simulated for shade leaves by increasing the leaf cuvette PPFD (LI-COR red/blue light source) to match the light environment of the full sun leaf in the same tree. The maximum sunfleck response of shade leaves was then recorded once CO~2~ and water vapor fluxes re-stabilized in the leaf cuvette (ca. 25 min).

@@

\
Unexpected higher rates of g~s~ in shade leaves compared to sun leaves led to decreased ITE in shade leaves throughout the experiment. Additionally, consistently higher leaf $\delta$^13^C in shade leaves suggests that this pattern was likely prevalent long term. From a canopy perspective this pattern in water-use efficiency initially appears to be detrimental to C gain as *A~n~* in sun leaves was characterized by low rates of g~s~ and low C~i~. Relative to the differences in *A~n~* between leaf types, higher rates of g~s~ in shade leaves appear to exhibit inefficient water use. As whole canopy C gain integrates the efficiency of all leaves, this begs the question of why shade leaves maintained a lower ITE compared to sun leaves.

>>>>

\
4. We predicted that climate warming would decrease g~s~ and leaf C gain in sun leaves more so than shade leaves during summer months, as increased evaporation demand from higher temperatures and irradiance lead to stomatal closure.

@@

\
Leaf level gas exchange was measured with a standard (2 x 3 cm) leaf cuvette using a portable gas exchange system (LI-6400XT, LI-COR, Lincoln, NE, USA). This system was coupled with a tunable diode laser (TDL; TGA100,Campbell Scientific, Inc., Logan, UT, USA) for concurrent measurements of online C isotope discrimination. The CO~2~ in the leaf cuvette was set at ambient atmospheric [CO~2~] (400 ppm) with a flow rate of 200 $\mu$mol s^-1^. We did not explicitly control relative humidity within the leaf cuvette. Two identical gas exchanges systems were run simultaneously, one in each of an AT or ET WTC. Leaf temperatures were controlled at the current AT or ET WTC air temperature, thus observed VPD is based on leaf temperatures in the cuvette. PPFD in the cuvette was set to match the individual light environment of each leaf type (explained above). Periods of high irradiance were simulated for shade leaves by increasing the leaf cuvette PPFD (LI-COR red/blue light source) to match the light environment of the full sun leaf in the same tree. The maximum sunfleck response of shade leaves was then recorded once CO~2~ and water vapor fluxes re-stabilized in the leaf cuvette (ca. 25 min).

@@

\
Unexpected higher rates of g~s~ in shade leaves compared to sun leaves led to decreased ITE in shade leaves throughout the experiment. As the VPD used to calculate ITE was recorded from controlled cuvette leaf temperatures, it is unknown if actual leaf temperatures varied within the canopy and how this could alter patterns in ITE. However, consistently higher leaf $\delta$^13^C in shade leaves suggests that the observed patterns in instantanesous ITE were likely prevalent long term. From a canopy perspective this pattern in water-use efficiency initially appears to be detrimental to C gain as *A~n~* in sun leaves was characterized by low rates of g~s~ and low C~i~. Relative to the differences in *A~n~* between leaf types, higher rates of g~s~ in shade leaves appear to exhibit inefficient water use. As whole canopy C gain integrates the efficiency of all leaves, this begs the question of why shade leaves maintained a lower ITE compared to sun leaves.
